---
title: "Llan Distribution in Wales"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```


## Load Data

`uk-towns.csv` is a file containing coordinates and meta data for all cities, towns and villages in the UK. Here I am only interested in Wales, therefore I have filtered the data to only include places within the country of Wales.
```{r}
UKTowns <- read.csv('uk-towns.csv')
UKTowns %>%
  filter(country=='Wales') -> WalesTowns
```

## Confirm that Llan is the most common prefix in Wales

In order to ensure that Llan is the most common prefix of place names in Wales, I have extracted the first for letters of every place name into a new column called prefix. I have also selected for only a few columns of interest. 

```{r}
WalesTowns %>%
  mutate(prefix = substr(WalesTowns$name, 1, 4)) %>%
  select('name', 'prefix', 'local_government_area', 'latitude', 'longitude') -> WalesTowns
```

## Summarising all of the place name prefixes in Wales

```{r}
WalesTowns %>%
  select(prefix) %>%
  mutate(number = 1) %>%
  group_by(prefix) %>%
  summarise_all(sum) %>%
  filter(number > 25) %>%
  ggplot(aes(x = reorder(prefix, number), y = number)) +
    geom_bar(stat = "identity",
             color="#2b8cbe",
             fill="#2b8cbe" ) + 
    ylab("") +
    xlab("") +
    ggtitle("Is Llan the most common placename in Wales?") +
    theme_bw() +
    theme(axis.line = element_line(colour = "black"),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.border = element_blank(),
      panel.background = element_blank())
```







